Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2022-06-03 analysis/paper/shceof.tex
Renderiza

\leavevmode\vadjust pre{\hypertarget{ref-era5}{}}%
Hersbach, H., B. Bell, P. Berrisford, G. Biavati, A. Horányi, J. Muñoz Sabater, J. Nicolas, et al. 2019. {``{Era5} Monthly Averaged Data on Pressure Levels from 1979 to Present.''} \emph{{Copernicus Climate Change Service} ({C3s}) {Climate Data Store} ({CDS})} (Accessed on {\(<\)}03-06-2022{\(>\)}). \url{https://doi.org/10.24381/cds.6860a573}.

>>>>

\leavevmode\vadjust pre{\hypertarget{ref-era5}{}}%
Hersbach, H., B. Bell, P. Berrisford, G. Biavati, A. Horányi, J. Muñoz Sabater, J. Nicolas, et al. 2019. {``{Era5} Monthly Averaged Data on Pressure Levels from 1979 to Present.''} \emph{{Copernicus Climate Change Service} ({C3s}) {Climate Data Store} ({CDS})} (Accessed on {\(<\)}07-09-2021{\(>\)}). \url{https://doi.org/10.24381/cds.6860a573}.
